% Created 2022-01-25 Tue 10:52
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{John Doe}
\date{\today}
\title{Disc2}
\hypersetup{
 pdfauthor={John Doe},
 pdftitle={Disc2},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.6)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

Hello everyone!
My major is nutrition, and some of the jobs I have looked at are Dietician, Sports Nutritionist, and Nutrition Consultent. This major is deisgned to prepare you for the graduate program in nutrition and dietetics. The goal of the graduate program is to eventually recieve the accreditation of Registered Dietitian Nutritionist. During this program you start doing hands-on work during your junior year, and will continue until the end of your fifth year in the program. This hands-on practice allows students like me to gain valuable experience within our own community in actual medial practice. As students we will also have the opportunity to mentor undergraduates, which will help us grow our own leadership skills in a job enironment.

When it comes to writing as a Dietician one of the most important documents will be meal plans or dietary restirictions before or after surgery. 
\end{document}
